A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-03 doc/popl2013/legion-types.tex
mostly-complete draft of language definition and typing rules
more stuff (not all of it good)

\bibliographystyle{plainnat}
\usepackage{amsmath,amsthm}
\usepackage{listings}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{cancel}

@@

\title{Legion: Expressing Locality and Independence with Logical Regions}
\authorinfo{}{}{}
\maketitle

\begin{abstract}
Limit is 12 pages, including bibliography and appendices.
Deadlines: \\

\begin{tabular}{ll}
Paper registration & July 7, 2012 3:59am PDT \\
Paper submission & July 11, 2012 3:59am PDT \\
Author response & September 10 - September 13, 2012 \\
Author notification & October 1, 2012
\end{tabular}
\end{abstract}

@@

>>>>

\bibliographystyle{plainnat}
\usepackage{amsmath,amsthm}
\usepackage{listings}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{cancel}
\usepackage{multirow}

@@

\title{A Type System for Safe and Scalable Parallelism using Logical Regions}
%\title{Scalable and Safe Parallelism using Logical Regions}
\authorinfo{}{}{}
\maketitle

\begin{abstract}
Legion is a programming model that introduces 
{\em logical regions} as a mechanism for targeting large heterogeneous machines 
with complex memory hierarchies.  Logical regions are a first-class 
feature of Legion that allow programmers to specify independence 
and locality properties of program data dynamically.  We present
a type and effect system for reasoning about logical regions in Legion.  
We prove a soundness result for our type system and use it to show
that all memory accesses in Legion are safe.  Futhermore, we prove that
the soundess of our type system enables a scalable hierarchical
scheduling algorithm for Legion programs.  We implement a type checker
for Legion programs and improve performance up to 85\% by eliding
unncessary memory checks.  We demonstrate an implementation of the Legion 
runtime based on the hierarchical scheduling algorithm scales for
three real-world applications.

%Limit is 12 pages, including bibliography and appendices.
%Deadlines: \\

%\begin{tabular}{ll}
%Paper registration & July 7, 2012 3:59am PDT \\
%Paper submission & July 11, 2012 3:59am PDT \\
%Author response & September 10 - September 13, 2012 \\
%Author notification & October 1, 2012
%\end{tabular}
\end{abstract}

@@

%\input{outline}

\input{langdef}
